%% uctest.tex 11/3/94
%% Copyright (C) 1988-2004 Daniel Gildea, BBF, Ethan Munson.
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License, either version 1.3
% of this license or (at your option) any later version.
% The latest version of this license is in
%   http://www.latex-project.org/lppl.txt
% and version 1.3 or later is part of all distributions of LaTeX
% version 2003/12/01 or later.
%
% This work has the LPPL maintenance status "maintained".
% 
% The Current Maintainer of this work is Daniel Gildea.
%
% 2007/08/01
% LaTeX Package "ucr" is modified from LaTeX package "ucthesis."
% This modification is therefore under to the conditions of 
% the LaTeX Project Public License.
% Its formality is suitable for the dissertation of University of
% California, Riverside.
% This test document is for the convenience of all students of
% University of California, Riverside.
% Contact Charles Yang at chcyang@yahoo.com if you like.
% Charles Yang has nothing to do with the original author's sarcasm.
%
%\documentclass[11pt]{ucthesis}
%\documentclass[11pt]{ucr}
\documentclass[oneside,final,letterpaper]{ucr}
\def\dsp{\def\baselinestretch{2.0}\large\normalsize}
\dsp
%\documentclass[11pt]{book}
\begin{document}
%Declarations for Front Matter

\title{Search for Supersymmetry in Proton-Proton Collisions at a Center-of-Mass Energy of 13 TeV with a Customized Top Quark Tagger in the All-Hadronic Final State}
\author{Hua Wei}
\degreemonth{December}
\degreeyear{2017}
\degree{Doctor of Philosophy}
\chair{Prof. John William Gary}
\othermembers{Prof. Haibo Yu\\Prof. Owen Long}
\numberofmembers{3}
\field{Physics}
%\field{Experimental High Energy Particle Physics}
\campus{Riverside}

\maketitle
\copyrightpage{}
\approvalpage{}

\degreesemester{Fall}
\begin{frontmatter}

\begin{acknowledgements}
Now it is the end of this adventure. It is a just a small one, comparing with the big world. But, I can hardly survive without the supports of my colleagues and friends. I owe a lot of thanks since I left CERN in a hurry. 

First, I would like to give a big thank you to my advisor, Bill. I can hardly to have such a good chance to work at CERN, with CMS HCAL guys and on SUSY analysis, without his support. He also put huge efforts to help me to improve the quality of thesis, which I am really appreciated. He helps a lot on both academic work and real life issue. Our UCR sub-group meeting, hosting by Bill and Owen on weekly basis, is a great place to share working progress and ideas. I benefit a lot from the reports and discussions from Florent, Amin and Georgia in the meeting. 

Working on CMS detector is not easy. A new member working on the detector is just like a new swimmer struggling in the sea. But, I am lucky enough to have some nice guys supporting me when I am drowning. Jared is the guy who helps me to start the HCAL related work at very beginning. I work under Dick's guidance after Jared left. Dick is a real expert on HCAL. It is indeed a great honor to work with him. I hope I can be a person like him in future: leading the work, helping young people. Josh, I cannot remember how many times we work together to deal with HCAL in the midnight. I bet you will miss me also, especially when you are trying to find someone to practice Chinese in the intervals of operation work. Edmund helps a lot on dealing with the damn HO mapping. I was impressed by his extremely high profile skill in coding. Ted L helps me a lot on the map fiber id checking. His cool head and professional attitude is always valuable. Seth, John and Martin, I will never forget the days we work together: we are waked up in the mid-night, debugging on the HCAL, and finally fixed the issue. 

The analysis work is also challenging, especially to a beginner. However, I am just so lucky to have Florent and Hongxuan as analysis conveners. They answered tons of rudimental questions from me when I was starting the analysis work. They also gave me a lot of good advises when I was getting stuck on work. Kenichi's serious and tireless attitudes on the work are highly respectful in the group. I benefit a lot from his wide knowledge on both physics analysis and detector. It is a great honor to work with all the stop team alpha members: Zhenbin, Joe, Nadja, Scarlet, Koushik, Joshi, Hui, etc. I indeed learned a lot from your folks. 

Life in Geneva is wonderful, peaceful and productive. However, it was a bit sad to leave my friend in Riverside and move to Geneva at the beginning. Mingjian and Peng are my primary roommates at CERN. I knew them since I was an undergraduate student. It was a great reunion, until they passed away in a car accident in 2015. There are lots of words I want to but have no chance to tell them. 

Fortunately I still have friends to support each other, in both daily life and work. Menglei is such a great friend. It is always pleasant when talking with her, on both daily life and physics topics (ECAL, DQM, SUSY, etc.). Manuel is my last office mate. I was lucky to catch his defense before he move on to his new post-doc job. Huilin is a friend and an ``enemy". He works on stop search team A, a great competitor. We are did not exchange much idea on physics until my last year. I benefit a lot from him on the discussion of convolutional neural network. Hualin is a reliable friend. It is always a pleasure to chat with him on various topics, like CSC, Higgs to ZZ 4 lepton analysis, etc. He also help on to babysitter my car when I left the town. 

One of the most interesting things at CERN is that you can always find someone to have physics night after party. I always remember Qi (Atlas), Xiangyang (Atlas), and Jingyu (CMS) had such a night together. We discuss various high-energy physics topics (and drinking) until 4:00 a.m. in the morning. I would also give a special thanks to Jingyu, for hosting me when I visit fermilab, it was indeed a good night for me (only) to watch Cavalry beat Warrior in the buffalo chicken wing, haha. 

Yali is my dearest friend. She always covered my back when I was on fire. Her professional knowledge on feminism (although I never take the whole package, haha) and other aspects of expertise in social science give me a brand new view of the world. I never feel tired when talking with her. 

Finally, my deepest appreciation belongs to my family, especially to my parents. Sometimes, it is just so supportive to know that there is a place I can always come back. 
\end{acknowledgements}
\begin{dedication}
\null\vfil
{\large
\begin{center}
%\usepackage{CJK}
%\begin{CJK}{GBK}{song}
To my beloved grandpa, who always encourages me to pursue science. But I lost him in my second year of Ph.D.
%中文测试
%\end{CJK}
\end{center}
}
\vfil\null
\end{dedication}
\begin{abstract}
	This thesis presents a search for direct and gluino-mediated production of supersymmetric scalar top-quark pairs in the all-hadronic final state using top quark tagging. The results of search are based on a sample of proton-proton collision events collected at a center-of-mass energy of 13 TeV with the CMS detector at the CERN Large Hadron Collider, corresponding to an integrated luminosity of 36 fb$^{-1}$. The results of the search are interpreted in several simplified models for supersymmetric particle production.
\end{abstract}
\tableofcontents
\listoffigures
\listoftables
\end{frontmatter}

%\part{First Part}
%introduce the common definition files
\input{pdefs}

\input{sections/c1_Introduction} %usually intro
\input{sections/c2_SMAndSUSY}
\input{sections/c3_LHCAndCMS}
\input{sections/c4_SUSYTopTaggerAnalysis}
\input{sections/c5_Conclusions}

\nocite{*}
% \singlespacing
% \bibliographystyle{alpha}
\bibliographystyle{plain}
\bibliography{reference}

\renewcommand{\theHchapter}{A\arabic{chapter}}
\appendix
\addtocontents{toc}{\protect\setcounter{tocdepth}{3}} 
\input{sections/AppendixA}
\input{sections/AppendixB}

\end{document}
